### 2023-01-26 manuscript.tex
Use  citation style as default
add keywords and student number
slight modification:

\documentclass[12pt]{report}
\usepackage[paperwidth=21cm,paperheight=29.7cm,left=2cm,right=2cm,top=3.5cm,bottom=1.5cm]{geometry}
% Originally this was \usepackage[paperwidth=19cm,paperheight=26cm,left=3cm,right=3cm,top=3.5cm,bottom=1.5cm]{geometry}
\addtolength{\voffset}{-1.5cm}
\renewcommand{\baselinestretch}{1.7}
\renewcommand{\abstractname}{\large Abstract}
\usepackage{setspace}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{kotex}

\usepackage{natbib}

@@

\setstretch{1.15}
\setlength{\parindent}{2em}
\setlength{\parskip}{0.5em}

@@

abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents 
\end{abstract}\setcounter{page}{5}

@@

\chapter{Summary and Future Works}
summary

Future works

\bibliographystyle{plain}
\bibliography{references.bib}
\addcontentsline{toc}{chapter}{Bibliography}

@@

>>>>

\documentclass[12pt]{report}
\usepackage[paperwidth=21cm,paperheight=29.7cm,left=2cm,right=2cm,top=3.5cm,bottom=1.5cm]{geometry}
% Originally this was \usepackage[paperwidth=19cm,paperheight=26cm,left=3cm,right=3cm,top=3.5cm,bottom=1.5cm]{geometry}

\addtolength{\voffset}{-1.5cm}
\renewcommand{\baselinestretch}{1.7}
\renewcommand{\abstractname}{\large Abstract}
\usepackage{setspace}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{kotex}
\usepackage[round]{natbib}

%\usepackage{hyperref}

@@

\setstretch{1.2}   % 1.2 is good because (1) it is not too large, but (2) large enough that a simple inline fraction ($\frac{num}{den}$) is well displayed.
\setlength{\parindent}{2em}
\setlength{\parskip}{0.5em}

@@

abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents abstract contents

~\\
\hangindent=2em
\hangafter=2
\textbf{Keywords}: Asteroids, Thermal modeling, Regolith, Radiation Pressure, Polarimetry---Optical, Polarimetry---Infrared

~\\
\noindent \textbf{\textit{Student Number}}: 2000-12345

\end{abstract}\setcounter{page}{5}

@@

\chapter{Summary and Future Works}
\input{chaps/sum}

This is how you put references:

\cite{1929PhDT.........9L,1970GeCAS...1.2127G,1986MNRAS.218...75G}

Inside the paretheses: \citep{2022_SAG_NICpolpy}

And with prefix/suffix: \citep[prefix!][suffix!]{2018AJ....156..123A}

\clearpage
\bibliographystyle{agsm}
\bibliography{references.bib}
\addcontentsline{toc}{chapter}{Bibliography}

@@

~\\
\hangindent=2em
\hangafter=2
\textbf{주\,요\,어}: 소행성, 열적 모델링, 표토, 복사압, 편광---광학, 편광---적외선

~\\
\noindent \textbf{학 \quad 번}: 2000-12345
